Community-Centric Innovation

### 2014-02-20 paper.tex
talking about qmp

Community wireless are particularly useful in underserved areas with little presence of commercial operators.
In rural, distant or poor areas community networks can be the only viable alternative to access the Internet.
In this places, the inhabitants have a strong incentive in spending time and energies in acquiring the necessary skills required to deploy and operate a network.

@@

>>>>

Community wireless are particularly useful in underserved areas with little presence of commercial operators.
In rural, distant or poor areas community networks can be the only viable alternative to access the Internet.
In these places, the inhabitants have a strong incentive to spend time and energies in acquiring the necessary skills required to deploy and operate a network.

@@

Compared to commercial Internet, Community Networks are more heterogeneous and decentralized.
As a consequence they have properties that complement those of commercial networks.
In case of natural disaster, having alternative resilient networks to coordinate rescue and humanitarian help can save lives.

Mesh technologies such as the \emph{quick mesh project} (qmp) are evolving to make it easier for regular citizens to set up a network in a matter of minutes.
Friendly web interfaces for configuration abstract the underlying technological complexity.
As a consequence, it is possible to deploy and maintain network connectivity even in the most adverse conditions.

The decentralized nature of community networks greatly helps in fostering organic growth and resisting node failures.
The absence of central points of failure guarantees that two neighbours will be able to connect to each other as long as they keep their nodes running, regardless of what happens to the rest of the network.
The dynamic routing protocols, such as BMX6 allows the network to quickly re-configure itself and route packets around failures to keep connectivity.
To take a community network down it is necessary to shut down all the nodes.

Community networks are often less stable and more dynamic that their commercial counterparts.
The participants of community networks are eager to experiment and evolve all aspects of the network even if this results in occasional connectivity cuts.
As an example, while commercial networks seem to have a hard time transitioning to IPv6, qmp networks are native IPv6 networks.
Protocols, firmware and topology change on a daily basis to fix bugs, improve the performance or adapt to new situations.

This continuous change represent a challenge for spying agencies interested in compromising the network.
It is much more difficult to attack up-to-date system that those that run old unpatched firmwares.

\subsection{Networked Cryptocurrencies}
